My title

### 2024-02-14 outputs/paper/paper.qmd
paper update

ggplot(state_score, aes(x = case_rate_per100k_zip, y = pass)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "COVID-19 Case Rate per 100k", y = "Passing Rate", 
       title = "Correlation between Passing Rate and COVID-19 Case Rate per 100k") +
  theme_minimal() +
  xlim(0, 350)

ggplot(state_score, aes(x = case_rate_per100k_zip, y = pass)) +
  geom_point() +  # Add points
  geom_smooth(method = "lm", se = FALSE) +  # Add a linear regression line without standard error bands
  labs(x = "COVID-19 Case Rate per 100k", y = "Passing Rate", 
       title = "Correlation between Passing Rate and COVID-19 Case Rate per 100k") +
  theme_minimal()
# Print the results of the correlation test

@@

1. Passing Rate Trends Over Different Years and Subjects: Figue [@fig] shows the decline in passing rates in English Language Arts (ELA) and Mathematics from 2016 to 2021, depicting a consistent downward trend across both subjects especially during pandemic period from 2019 to 2021.

@@

Building on these overviews, we visualized the distribution of learning models across states using box plots. The box plot for in-person learning [@box_plot_inperson] revealed a range of engagement across states, with Virginia showing a median of 0 percentage in-person learning during 2019 to 2021, whereas Wyoming having a median of approximately 80 percent in-person learning. The virtual learning model box plot [@box_plot_virtual] showed a significant number of outliers, suggesting that certain states had districts with a notably high share of virtual learning.The states Wyoming and Rhode Island had a median of 0 percent virtual learning whereas Virginia had highest median of virtual learning.  Lastly, the hybrid learning model [@box_plot_hybrid] box plot displayed variability, with some states having a wide interquartile range, showing a diverse adoption of this learning model. However, Colorado had a median of 0 percent adoption of hybrid learning model relative to other states. These visual insights set the foundation for further statistical examination in subsequent analyses.

Following the initial box plots, we continued our investigation with a scatter plot [@scatterplot] and examined the relationship between the share of virtual learning and student passing rates. The scatter plot indicates a downward trend, with a line suggesting that an increase in the share of virtual learning correlates with a decrease in passing rates. The data points suggest that higher virtual learning is associated with lower academic performance of students.

>>>>

ggplot(state_score, aes(x = case_rate_per100k_zip, y = pass)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "COVID-19 Case Rate per 100k", y = "Passing Rate", 
       title = "Correlation between Passing Rate and COVID-19 Case Rate per 100k") +
  theme_minimal() +
  xlim(0,100)

filtered_data <- state_score %>%
  filter(year %in% c(2019, 2021))

# Now create the scatter plot with the filtered data
ggplot(filtered_data, aes(x = case_rate_per100k_zip, fill = as.factor(year))) +
  geom_density(alpha = 0.5) +  # Adjust transparency with alpha
  labs(x = "COVID-19 Case Rate per 100k", y = "Density",
       title = "Density Plot of COVID-19 Case Rates per 100k (2019 vs 2021)",
       fill = "Year") +
  theme_minimal()

@@

1. Passing Rate Trends Over Different Years and Subjects: Figure [@fig] shows the decline in passing rates in English Language Arts (ELA) and Mathematics from 2016 to 2021, depicting a consistent downward trend across both subjects especially during pandemic period from 2019 to 2021.

@@

Building on these overviews, we visualized the distribution of learning models across states using box plots. The box plot for in-person learning [@box_plot_inperson] revealed a range of engagement across states, with Virginia showing a median of 0 percentage in-person learning during 2019 to 2021, whereas Wyoming having a median of approximately 80 percent in-person learning.

The virtual learning model box plot [@box_plot_virtual] showed a significant number of outliers, suggesting that certain states had districts with a notably high share of virtual learning.The states Wyoming and Rhode Island had a median of 0 percent virtual learning whereas Virginia had highest median of virtual learning.  Lastly, the hybrid learning model [@box_plot_hybrid] box plot displayed variability, with some states having a wide interquartile range, showing a diverse adoption of this learning model. However, Colorado had a median of 0 percent adoption of hybrid learning model relative to other states. These visual insights set the foundation for further statistical examination in subsequent analyses.

After assessing the distribution of in-person, virtual, and hybrid learning models across states, we narrowed our focus to further investigate the impact of virtual learning, as this model showed a significant variation and prevalence during the pandemic period. We plotted a scatter plot [@scatterplot] and examined the relationship between the share of virtual learning and student passing rates. The scatter plot indicates a negative trend, which implies that an increase in the share of virtual learning correlates with a decrease in passing rates. The data points suggest that higher virtual learning is associated with lower academic performance of students.
